---
title: "homework4stat631"
author: "Jessica Grover"
date: "4/21/2022"
output:
  pdf_document: default
  word_document: default
---

# Problem 10.3
```{r}
library(tidyverse)
rating <- c(3.5, 3.6, 2.1, 4.0, 3.1,
3.0, 2.9, 4.5, NA, NA,
7.2, 6.8, 6.7, 7.5, 6.8,
NA, NA, 4.8, 6.9, 9.3,
4.1, 5.8, 4.5, 5.3, 4.1,
5.6, 4.8, 4.6, 7.3, 5.3,
5.3, 4.8, 5.0, 6.7, 5.2,
NA, 3.2, 7.2, 6.7, 4.2,
4.5, 5.1, 5.0, 4.9, 4.5,
2.7, 3.7, 4.5, 4.7, NA)
protein <- rep(1:5, 5) %>% as.factor()
gum <- rep(1:5, each = 10) %>% as.factor()
icecream <- data.frame(rating, protein, gum) %>% na.omit(icecream)
head(icecream)
```
```{r}
library("car")
model1 <- lm(rating ~ protein*gum, data = icecream)
Anova(model1, type = "II")
```
Hypothesis for protein:
H0: a=0
H1: a> 0

We have p-value of protein is 0.1894 > 0.05, we failto reject the null hypothesis, protein has no significant
eect on the sensory rating.
Hypothesis for gum:
H0: b=0
H1: b> 0
We have p-value of gum is ¥ 0 < 0.05, we can reject the null hypothesis, so the data gave proficient proof
that gum has significant eect on the sensory rating.
Determine which, if any, proteins and/or gums dier in their sensory ratings.

```{r}
library(emmeans)
lsmGum <- lsmeans(model1, ~ gum)
TkGum <- summary(contrast(lsmGum, method="pairwise", adjust="tukey"))
TkGum
```

From the Tukey contrast table, we have the contrast of group 2 vs others have p-values :
1 - 2: 0.0001
2 - 3: 0.0109
2 - 4: 0.0365
2 - 5: 0.0007
The p-values are < 0.05, So we can conclude the group 2 is significantly dierent with other group in
sensory ratings.

------------------------------------------------------------------------------------
#Exercise 11.6

```{r}
a<- 30:50
crt <- 1/(1+2)*qf(0.99,a-1,a)
power<- 1-pf(crt,a-1,a)
plot(a,power)
abline(h=0.9)
```
```{r}
a=45
crt <- 1/(1+2)*qf(0.99,a-1,a)
power<- 1-pf(crt,a-1,a)
power
```
Summary: we need 45 individuals to achieve the 90% power given that the significance level of 0.01 and for alternative hypothesis.

------------------------------------------------------------------------------------
# Problem 11.2

```{r}
a <- c(2200, 2200, 2600, 2500, 1900, 2100, 2600, 4300, 4000, 3900,
3000, 2900, 3600, 3500, 2500, 2200, 2800, 1800, 4800, 4800,
210, 200, 290, 240, 160, 200, 330, 340, 370, 340,
270, 260, 360, 380, 230, 230, 350, 290, 500, 480)
pull <- data.frame(y=a,medical = factor(rep(1:4,each = 10)),load=factor(rep(rep(1:5,each=2),4)))

```
```{r}
with(pull,interaction.plot(x.factor = medical,trace.factor = load,response = y))

```
```{r}

library(lmerTest)

```

```{r}
library(lme4)
lm1 <- lmer(a~1+(1|medical)+(1|load)+(1|load:medical),data = pull)
ranova(lm1)
```

grandmean = 1 fixed effect of 1 is 5 and fixed effect of 2 is 4,degree of freedom (1) = 4;degree of freedom for (2) is 3. random effect = 20,degree of freedom for random effect is 4*3 = 12 sample = 40,degree of freedom for total sample equal to 40-1-4-3-12=20