---
title: "Hm3stat631"
author: "Jessica Grover"
date: "3/1/2022"
output:
  word_document: default
  pdf_document: default
---
#Problem 2
Reading the table
```{r}
cars<-read.table("car.dat",header = TRUE)
cars
```
#a.
```{r}

cars$ftype<-as.factor(cars$type)
cars

```
```{r}
model1<-lm(response~ftype,data=cars)
anova(model1)
```

The null hypothesis is rejected. There is a significant differance between means oil use in given cars as p-value is less than 0.05. Hence we can conclude that data provides significant evidence that there is a difference in the mean oil use of the cars.


#b.
```{r}
library(emmeans)
lsmcars<-lsmeans(model1,~ftype)
print(lsmcars)
```
```{r}
levels(cars$ftype)
```
#b1.
```{r}
contrast(lsmcars,list("ImportedWithExported"=c(-1/4,-1/4,1/2,-1/4,-1/4,1/2)))
```

```{r}
summary(contrast(lsmcars,list("ImportedWithExported"=c(-1/4,-1/4,1/2,-1/4,-1/4,1/2))),infer=c(T,T),level=0.95,side="two-sided")
```
Since we have interval of (0.506,0.932), it is clear that there is no 0. It means, the usage of oils of imported cars is more than the exported cars.

#b2.
```{r}
contrast(lsmcars,list("CheapWithExpensive"=c(1/3,1/3,1/3,-1/3,-1/3,-1/3)))
```
```{r}
summary(contrast(lsmcars,list("CheapWithExpensive"=c(1/3,1/3,1/3,-1/3,-1/3,-1/3))),infer = c(T,T),level = 0.95,side="two-sided")
```
Since the interval is (-0.967,-0.565), it does not involve 0. The value is negative so we can conclude that oil usage of cheaper cars are less than the expensive cars.
