---
title: "quiz2stat631"
author: "Jessica Grover"
date: "3/24/2022"
output:
  word_document: default
  pdf_document: default
---
#a.Construct the side-by-side boxplot to compare lengths of time among different types of cars and write down your observations.
```{r}
d1<-read.csv("CarRental.csv",header = TRUE)
library(emmeans)
head(d1)
d1$ftrt<- as.factor(d1$ind)
boxplot(values~ftrt, data = d1)
```
The box plot above confirms that the time taken by the compact is lowest and the time taken by the minivan is the largest.

#b. Is there any statistical evidence that different types of cars are rented for varying lengths of time? Perform the corresponding test and report your conclusions.
```{r}
model1<-lm(values~ftrt,data=d1)
anova(model1)
```
The p-value is less than 0.05, so we are rejecting the null hypothesis. We are 95% confident that there is atleast one difference in the rental car's length of time.
```{r}
plot(model1,which=2)
```
The above plot concludes that assumptions seems to be reasonable.


#C.Apply Tukey’s simultaneous confidence interval method with α = 0.05 to find the type of cars that has the shortest rental time and the type of cars that has the largest rental time.
```{r}
library(emmeans)
lsm1<- emmeans(model1, ~ftrt)
tk<- summary(contrast(lsm1,method="pairwise",adjust="tukey"),infer=c(T,T),level=0.95,side="two-sided")
tk
```
It is seen that luxury cars has shortest rental time. Minivan has the highest rental time because zero not included and it means that population parameters are highly significant


#d. Check the assumptions of your model. Are the conclusions from your model valid?
```{r}
library(car)

#summary(mod)
qqPlot(model1$residuals)
shapiro.test(model1$residuals)
```
```{r}
plot(model1$fitted.values,model1$residuals)

```
There is  constant variance so it  does not violates the assumption of variance.

